---
title: "Ch2_DataAnalysis"
author: "Esteban Agudo"
date: "2023-08-21"
output: html_document
---
#TEMPERATURE EFFECT ON PREDATION IN THE GALAPAGOS

In this study we measured the role of temperature on moderating predation in a system exposed to seasonal upwelling, The Galapagos.


Packages
```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library("rnaturalearth")
library("rnaturalearthdata")
library("sf")
library("ggspatial")
library(tidyverse)
library(sf)
library(wesanderson)
library(gridExtra)
library(ggpubr)
```


## Study Location Map Map

Loading file
```{r, warning=FALSE, message=FALSE}
shp_islas <-  read_sf("ShapeIslas/islas.shp")
Barcaza<-read.csv(file="Map.csv", header=T)

pal <- wes_palette("Zissou1", 100, type = "continuous")
```

```{r, warning=FALSE, message=FALSE}
#Select San Cristobal Area 
SanCristobal<-data.frame(x=c(-89.70, -89.2, -89.2, -89.7), y= c(-0.65, -0.65, -0.98, -0.98))

## Let's create a data frame with coordinates for arectangle for San Cristobal

#Let's make galapagos map
GalapagosMap<-ggplot(data = shp_islas)+ 
  geom_sf(color=NA)+
  #let's limit the map area
  coord_sf(xlim = c(-92, -89), ylim = c(-1.5, 0.5), 
           expand = FALSE)+
  #let's add a north arrow
  theme_bw()+ 
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(), 
        axis.text=element_blank(),
        axis.ticks = element_blank(),
        panel.grid.major = 
          element_line(colour = "white"),
        panel.grid.minor = 
          element_line(colour = "white"),
          panel.border = element_rect(colour = "darkslategray", fill=NA, size=0.1))+
 geom_polygon(data=SanCristobal, aes(x=x, y=y), color="red", alpha=0.2)

#GalapagosMap


LaBarcaza<-ggplot(data = shp_islas)+ 
  geom_sf(color=NA)+
  #let's limit the map area
  coord_sf(xlim = c(-89.70, -89.2), ylim = c(-1, -0.6), 
           expand = FALSE)+
  geom_point(data=Barcaza, 
             aes(x=Longitude, y=Latitude),
             alpha = 0.8, size=1, hjust=0.5)+
  geom_text(data=Barcaza, 
             aes(x=Longitude, y=Latitude, label=Locality), color = "darkslategray", size = 3.5, hjust=1, vjust=-0.5)+
  #scale_size(range = c(1,3))+
  theme_bw()+ 
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
      axis.ticks = element_blank(),
    panel.grid.major = element_line(colour = "white"), legend.position="none")


Map_Barcaza<-
LaBarcaza+annotation_custom(grob = ggplotGrob(GalapagosMap),
                    xmin=-89.70, xmax=-89.49, ymin=-0.76, ymax=-0.60)


#Figure 1: Study location 
png("Figures/Fig1_Map.png", width=22, height=13, units="cm", res=300)
print(Map_Barcaza)
dev.off()
```


## Temperature variation in La Barcaza

We are building a figure were we showed temperature variation in la Barcaza for one year

```{r, warning=FALSE, message=FALSE}

library(lubridate)
Barcaza_Temp<-read.csv("TemperatureBarcaza.csv", header=TRUE)
str(Barcaza_Temp)
#we need to define Barcaza_Temp as a time factor

Barcaza_Temp$DateTime<-as.POSIXct(Barcaza_Temp$time,
                                   format = "%m/%d/%Y %H:%M") # to keep only the day 
str(Barcaza_Temp)

library(plyr)
Barcaza_Temp$Temperature<-round_any(Barcaza_Temp$temp, 0.5)


#another way to separete in case we want to separate day and time 
#Barcaza_Temp<- Barcaza_Temp %>%
#  separate(Barcaza_Temp, time, c("date", "time"), sep = " ")

#daily_Barcaza_Temp<-Barcaza_Temp %>%
 # group_by(day) %>%
  #summarise(daily_temp=mean(temp))

Temp_Barcaza<-
  ggplot(Barcaza_Temp, aes(x=DateTime, y=Temperature, na.rm=TRUE))+
  geom_jitter(size=0.5, na.rm=TRUE, height = 0.15, alpha=0.3)+ 
  geom_smooth(method = "loess", se = FALSE, na.rm=TRUE, color="red3", size=2)+
  theme_classic()+ 
  theme(panel.background = element_blank())+
  xlab("")+
  ylab(expression("Temperature ("*~degree*C*")"))+
  scale_y_continuous(limits = c(14, 32), breaks = seq(14, 32, 2))

Temp_Barcaza

#Figure 2: Temperature variation in la Barcaza
png("Figures/Fig2_Temperature.png", width=22, height=13, units="cm", res=300)
print(Temp_Barcaza)
dev.off()
```

## Modeling the effect of temperature on predation and movement in the lab
```{r, warning=FALSE, message=FALSE}
lab_exp<- read.csv("LabPredation.csv", header=TRUE)
head(lab_exp)

#lets visualize data
boxplot(lab_exp$BarnacleEatenPerDay~lab_exp$Treatment, las=1, ylab="Barnacle per day", xlab="Temperature Treatment", main="Barnacle eaten per Temperature")
```

### Model effect of temperature on lab predation rates

```{r, warning=FALSE, message=FALSE}
model_poisson<-glm(BarnacleEaten~Treatment+offset(log(DaysExperiment)), family=poisson(link="log"), data=lab_exp) # we use offset because Poisson model only can consider number without decimals
summary(model_poisson)


model_gamma<-glm((BarnacleEatenPerDay+0.001)~Treatment-1, family=Gamma(link="log"), data=lab_exp) # gamma model cannot consider 0
summary(model_gamma)

library(jtools)
plot_summs(model_gamma, scale=TRUE, exp=TRUE) # Lets see effect with confidence intervals
```
The Gamma models seems to have a lower AIC so is the model we will be using 

Interval confidence
```{r, warning=FALSE, message=FALSE}
# Estimating the confidence intervals and estimate for plotting 
confint_gamma<-exp(confint(model_gamma, level = 0.95))

coefficient_gamma<-as.data.frame(exp(model_gamma$coefficients))

data_model<-cbind(coefficient_gamma, confint_gamma)
colnames(data_model)<-c("Estimate", "upr", "lwr")
rownames(data_model)<-c("16C", "21C", "26C", "28C")
data_model$Treatment <- rownames(data_model)
head(data_model)
```
Plotting model with interval confidence 

```{r, warning=FALSE, message=FALSE}
library(ggplot2)

colour.palette <- c("#332288", "red3", "#E69F00", "#117733", "#56B4E9","#E69F00",  "#CC79A7", "#D55E00", "#0072B2", "#F0E442", "#CC6677")

model_plot<-ggplot()+ 
    geom_point(data=data_model, aes(x=Treatment, y=Estimate), shape="-", size = 20, position = position_dodge(width = 0.85))+
    geom_errorbar(data=data_model, aes(x=Treatment, ymin=lwr, ymax=upr, colour=Treatment),  size = 8, width = 0, alpha = 0.6, position = position_dodge(width = 0.85), show.legend = FALSE)+
    geom_jitter(data=lab_exp, aes(x=Treatment, y=BarnacleEatenPerDay, colour=Treatment), size=1.5, alpha=0.5, position = position_jitterdodge(jitter.width = 0.1, jitter.height = 0.02, dodge.width = 0.85))+
    theme_classic()+
    theme(panel.border = element_rect(colour = "black", fill=NA, size=0.7),
        legend.position="none") +     
  ylab("Predation rate (Banacle eaten per day)")+
    xlab("Temperature treatment")+
  scale_y_continuous(limits = c(-0.05, 0.85), breaks = seq(0, 85, 0.2))+
    annotate("text",
           x = 1,
           y = 0.2,
           label = "a",
           family = "", fontface = 3, size=3)+
     annotate("text",
           x = 2,
           y = 0.8,
           label = "b",
           family = "", fontface = 3, size=3)+
   annotate("text",
           x = 3,
           y = 0.4,
           label = "a,b",
           family = "", fontface = 3, size=3)+
   annotate("text",
           x = 4,
           y = 0.53,
           label = "a,b",
           family = "", fontface = 3, size=3)+
  scale_colour_manual(values=colour.palette)

model_plot
```


### Modelling effect of temperature on movement
```{r, warning=FALSE, message=FALSE}
lab_exp<- read.csv("LabPredation.csv", header=TRUE)
head(lab_exp)
str(lab_exp)
#lets visualize data
boxplot(lab_exp$MovementPerDay~lab_exp$Treatment, las=1, ylab="Barnacle per day", xlab="Temperature Treatment", main="Barnacle eaten per Temperature")
```

Modelling effect of temperature on movement
```{r, warning=FALSE, message=FALSE}
model_poisson_mov<-glm(Movement~Treatment+offset(log(DaysExperiment)), family=poisson(link="log"), data=lab_exp) # we use offset because Poisson model only can consider number without decimals
summary(model_poisson)

model_gamma_mov<-glm((MovementPerDay)~Treatment-1, family=Gamma(link="log"), data=lab_exp) # gamma model cannot consider 0
summary(model_gamma_mov)

plot_summs(model_gamma_mov, scale=TRUE, exp=TRUE) # Lets see effect with confidence intervals
```

```{r}
confint_gamma<-exp(confint(model_gamma_mov, level = 0.95))

coefficient_gamma<-as.data.frame(exp(model_gamma_mov$coefficients))

data_model<-cbind(coefficient_gamma, confint_gamma)
colnames(data_model)<-c("Estimate", "upr", "lwr")
rownames(data_model)<-c("16C", "21C", "26C", "28C")
data_model$Treatment <- rownames(data_model)
head(data_model)

```
```{r}
model_plot_mov<-ggplot()+ 
    geom_point(data=data_model, aes(x=Treatment, y=Estimate), shape="-", size = 20, position = position_dodge(width = 0.85))+
    geom_errorbar(data=data_model, aes(x=Treatment, ymin=lwr, ymax=upr, colour=Treatment),  size = 8, width = 0, alpha = 0.6, position = position_dodge(width = 0.85), show.legend = FALSE)+
    geom_jitter(data=lab_exp, aes(x=Treatment, y=MovementPerDay, colour=Treatment), size=1.5, alpha=0.5, position = position_jitterdodge(jitter.width = 0.1, jitter.height = 0.02, dodge.width = 0.85))+
    theme_classic()+
    theme(panel.border = element_rect(colour = "black", fill=NA, size=0.7),
        legend.position="none") +     
  ylab("Movement (Position changes per day)")+
    xlab("Temperature treatment")+
  scale_y_continuous(limits = c(-0.05, 1.3), breaks=seq(0, 1.3, 0.2))+
    annotate("text",
           x = 1,
           y = 0.4,
           label = "a",
           family = "", fontface = 3, size=3)+
     annotate("text",
           x = 2,
           y = 1.14,
           label = "b",
           family = "", fontface = 3, size=3)+
   annotate("text",
           x = 3,
           y = 1.14,
           label = "b",
           family = "", fontface = 3, size=3)+
   annotate("text",
           x = 4,
           y = 1.11,
           label = "b",
           family = "", fontface = 3, size=3)+
   scale_colour_manual(values=colour.palette)


model_plot_mov
```


### Effect of temperature on movement and predation

```{r}
library(ggpubr)

temp_movement_feeding<-ggarrange(model_plot_mov, model_plot,
          labels = c("A", "B"),
          ncol = 2)

temp_movement_feeding

#Figure 3: Effect of temperature on whelk movement and feeding rates  
png("Figures/Fig2_TempertureMovementFeeding_Lab.png", width=22, height=15, units="cm", res=300)
print(temp_movement_feeding)
dev.off()
```

### Run bootstraping for lab experiment 
I will try to run the code for bootstraping the data

```{r, warning=FALSE, message=FALSE}
set.seed(16)
### Setup the bootstrap function and number of iterations
# This is a bootstrap function that will sample WITH replacement (explained step by step within the function)
bootFUN <- function(model, newdata) {
  if(class(model)[1] == "negbin"){
    nr <- nrow(model[["model"]]) # count number of rows in the model (# of observations)
    data <- model[["model"]] # pull data from model
  } else {
    nr <- nrow(model$data) # count number of rows in the model (# of observations)
    data <- model$data # pull data from model
  }
  data2 <- data.frame(data[sample(1:nr, replace = TRUE), ]) # random sample of numbers from 1 - nr (# of rows) to select data from
  update <- update(model, data = data2) # rerun the model using the 'new' dataset from the random smapling above
  predict(update, newdata, type = "response", level = 0.95) # predicts response variable with model and updated data 
}

bootnum <- 1000 #Number of boostraping 

#The model we will use 

model_gamma<-glm((BarnacleEatenPerDay+0.001)~Treatment-1, family=Gamma(link="log"), data=lab_exp) # gamma model cannot consider 0
summary(model_gamma)

#the data 
newdata <- data.frame(Treatment = lab_exp$Treatment)

boot <- replicate(bootnum, bootFUN(model = model_gamma, newdata = newdata)) # run the bootFUN the number (bootnum) of times specified and save as matrix

#error 

```



## Effect of temperautre on whelk predation rates on the field 
```{r}
field_exp<- read.csv("FieldPredation_BarcazaExp.csv", header=TRUE)
head(field_exp)

#lets visualize data
boxplot(field_exp$DailyPredation~field_exp$Treatment*field_exp$Temperature, las=1, ylab="Barnacle per day", xlab="Temperature Treatment", main="Barnacle eaten per Temperature")
```
### Modelling effect of temperature on Field predation rates

```{r}
#we need to make temperautre a factor

field_exp$Temperature<-as.factor(field_exp$Temperature)

#model_poisson<-glm(BarnacleEaten~Treatment+offset(log(DaysExperiment)), family=poisson(link="log"), data=lab_exp) # we use offset because Poisson model only can consider number without decimals
#summary(model_poisson)

model_gamma_field<-glm((DailyPredation+0.01)~Treatment:Temperature-1, family=Gamma(link="log"), data=field_exp) # we add 0.01 so we don't have zeros 
summary(model_gamma_field)

confint_gamma<-exp(confint(model_gamma_field, level = 0.95))


plot_summs(model_gamma_field, scale=TRUE, exp=TRUE) # Lets see effect with confidence intervals
```

Lets calculate and determine the coefficients and confint for building the plot
```{r, message=FALSE, warning=FALSE}
confint_gamma<-exp(confint(model_gamma_field, level = 0.95))

coefficient_gamma<-as.data.frame(exp(model_gamma_field$coefficients))

data_model<-setNames(cbind(rownames(coefficient_gamma), coefficient_gamma, confint_gamma, row.names = NULL), 
         c("COL1", "estimate", "upr", "lwr")) # set colnames

# lets separate factors 
data_model<- gsub("Treatment|Temperature", "", data_model$COL1)%>%      
  str_split(":", simplify = TRUE)%>% 
  as.data.frame() %>% cbind(data_model)  
  
#select only the columns we are interested in 
data_model<-data_model %>%
  select(V1, V2, estimate, upr, lwr)


#lets assign names to the columns 
  colnames(data_model)<-c("Predation", "Temperature", "Estimate", "upr", "lwr") 

head(data_model)
```

```{r}
model_field_pred<-ggplot()+ 
    geom_point(data=data_model, aes(x=Temperature, y=Estimate, colour=Predation), shape="-", size = 20, position = position_dodge(width = 0.85))+
    geom_errorbar(data=data_model, aes(x=Temperature, ymin=lwr, ymax=upr, colour=Predation),  size = 8, width = 0, alpha = 0.6, position = position_dodge(width = 0.85), show.legend = FALSE)+
    geom_jitter(data=field_exp, aes(x=Temperature, y= DailyPredation, colour=Treatment), size=1.5, alpha=0.5, position = position_jitterdodge(jitter.width = 0.05, jitter.height = 0.02, dodge.width = 0.95))+
    theme_classic()+
    theme(panel.border = element_rect(colour = "black", fill=NA, size=0.7),
    #legend.position = "right",
    legend.position = c(0.90, .75),
     #legend.direction = "vertical",
     #legend.justification = c("left", "bottom"),
     #legend.box.just = "left",
     legend.margin = margin(0, 0, 0, 0),
     legend.box.spacing = unit(0, "pt"),
     legend.spacing.y = unit(0.5, "lines"),
      legend.text = element_text(size = 7.5, family = "Arial"),
      legend.key.size = unit(0.05, "cm"),
       ) +     
  ylab("Predation rate (Barnacles eaten per day)")+
    xlab("Temperature treatment")+
  labs(color=NULL)+
  scale_y_continuous(limits = c(-0.05, 1), breaks=seq(0, 1, 0.2))+
    annotate("text",
           x = 0.72,
           y = 0.17,
           label = "a",
           family = "", fontface = 3, size=3)+
     annotate("text",
           x = 1,
           y = 0.55,
           label = "b",
           family = "", fontface = 3, size=3)+
   annotate("text",
           x = 1.26,
           y = 0.45,
           label = "b",
           family = "", fontface = 3, size=3)+
   annotate("text",
           x = 2,
           y = 0.42,
           label = "b",
           family = "", fontface = 3, size=3)+
  annotate("text",
           x = 2.26,
           y = 0.88,
           label = "b",
           family = "", fontface = 3, size=3)+
     annotate("text",
           x = 2.7,
           y = 0.10,
           label = "a",
           family = "", fontface = 3, size=3)+
   annotate("text",
           x = 3,
           y = 0.35,
           label = "b",
           family = "", fontface = 3, size=3)+
   annotate("text",
           x = 3.24,
           y = 0.3,
           label = "b",
           family = "", fontface = 3, size=3)+
   scale_colour_manual(values=colour.palette)


model_field_pred


#MODEL WITHOUTH PILOT DATA (PILOT DATA DOES NOT HAVE ONE OF THE TREATMENT AND REPLICATION IS VERY LIMITED) 

data_model2<-data_model %>%
  filter(!Temperature=="24")

field_exp2<-field_exp %>%
  filter(!Temperature=="24")

model_field_pred2<-ggplot()+ 
    geom_jitter(data=field_exp2, aes(x=Temperature, y= DailyPredation, colour=Treatment), size=1.5, alpha=0.5, position = position_jitterdodge(jitter.width = 0.01, jitter.height = 0.02, dodge.width = 0.85))+
  geom_point(data=data_model2, aes(x=Temperature, y=Estimate, colour=Predation), shape="-", size = 20, position = position_dodge(width = 0.85))+
    geom_errorbar(data=data_model2, aes(x=Temperature, ymin=lwr, ymax=upr, colour=Predation),  size = 8, width = 0, alpha = 0.6, position = position_dodge(width = 0.85), show.legend = FALSE)+
    theme_classic()+
    theme(panel.border = element_rect(colour = "black", fill=NA, size=0.7),
    legend.title=element_blank(),
    #legend.position = "right",
    legend.position = c(0.85, .9),
    legend.direction = "vertical",
    #legend.justification=c(0,0),
    #legend.justification = c("left", "bottom"),
   # legend.box.just = "left",
  #  legend.margin = margin(0, 0, 0, 0),
    #legend.box.spacing = unit(0, "pt"),
    # legend.spacing.y = unit(0, "lines"),
      legend.text = element_text(size = 9.5, family = "Arial"),
      legend.key.size = unit(0.1, "cm")
       ) +
    guides(color = guide_legend(override.aes = list(size = 5)))+ #this is really important to define size of figure in legend
  ylab("Predation rate (Barnacles eaten per day)")+
    xlab("Temperature")+
   scale_y_continuous(limits = c(-0.05, 0.6), breaks=seq(0, 0.6, 0.1))+
    annotate("text",
           x = 0.72,
           y = 0.15,
           label = "a",
           family = "", fontface = 3, size=3)+
     annotate("text",
           x = 1,
           y = 0.50,
           label = "b",
           family = "", fontface = 3, size=3)+
   annotate("text",
           x = 1.28,
           y = 0.42,
           label = "b",
           family = "", fontface = 3, size=3)+
  annotate("text",
           x = 1.72,
           y = 0.09,
           label = "a",
           family = "", fontface = 3, size=3)+
  annotate("text",
           x = 2,
           y = 0.34,
           label = "b",
           family = "", fontface = 3, size=3)+
  annotate("text",
           x = 2.27,
           y = 0.29,
           label = "b",
           family = "", fontface = 3, size=3)+
   scale_colour_manual(values=colour.palette)

 model_field_pred2    

 
#Figure 4: Effect of temperature on field whelk predation rates  
png("Figures/Fig4_TempertureFieldPredation.png", width=22, height=15, units="cm", res=300)
print(model_field_pred2)
dev.off()

```

#### Running bootstrap Colleen method
```{r, warning=FALSE, message=FALSE}
set.seed(16)
### Setup the bootstrap function and number of iterations
# This is a bootstrap function that will sample WITH replacement (explained step by step within the function)
bootFUN <- function(model, newdata) {
  if(class(model)[1] == "negbin"){
    nr <- nrow(model[["model"]]) # count number of rows in the model (# of observations)
    data <- model[["model"]] # pull data from model
  } else {
    nr <- nrow(model$data) # count number of rows in the model (# of observations)
    data <- model$data # pull data from model
  }
  data2 <- data.frame(data[sample(1:nr, replace = TRUE), ]) # random sample of numbers from 1 - nr (# of rows) to select data from
  update <- update(model, data = data2) # rerun the model using the 'new' dataset from the random smapling above
  predict(update, newdata, type = "response", level = 0.95) # predicts response variable with model and updated data 
}

bootnum <- 1000 #Number of boostraping 

#The model we will use 
model_gamma_field<-glm((DailyPredation+0.01)~Treatment:Temperature-1, family=Gamma(link="log"), data=field_exp) # we add 0.01 so we don't have zeros 
#the data 
newdata <- data.frame(Treatment = field_exp$Treatment, Temperature=field_exp$Temperature)

boot <- replicate(bootnum, bootFUN(model = model_gamma_field, newdata = newdata)) # run the bootFUN the number (bootnum) of times specified and save as matrix

#to find the estimate mean effect and the lower and upper confident intervals
field_exp_boot <- cbind(field_exp, as.data.frame(t(apply(boot, 1, function(x) c(quantile(x, c(0.025, 0.5, 0.975)))))))

colnames(field_exp_boot)[9:11] <- c("lowerci", "mean", "upperci") # rename mean/CI columns

str(field_exp_boot)
```

### Plotting model data from bootstraping
```{r, warning=FALSE, message=FALSE}
field_exp_boot<-field_exp_boot %>%
  filter(!Temperature=="24")

boot_plot <- ggplot() +
  geom_point(data = field_exp_boot, aes(x = Temperature , y = DailyPredation, colour = Treatment), shape = 1, alpha = 0.4, position = position_jitterdodge(jitter.width = 0.1, jitter.height = 0.05, dodge.width = 0.85)) +
  geom_linerange(data = field_exp_boot, aes(x = Temperature, ymin = lowerci, ymax = upperci, colour = Treatment), alpha = 0.1, size = 8, position = position_dodge(width = 0.85)) +
  geom_point(data = field_exp_boot, aes(x = Temperature, y = mean, colour = Treatment), shape = "-", size = 20, position = position_dodge(width = 0.85)) + # plots the mean value 
  theme_bw() +
  theme(panel.grid = element_blank(), panel.background=element_blank(), legend.key=element_blank(), strip.background = element_blank())+
  scale_colour_manual(name = "", values = colour.palette) + # adds the colours for plotting
  #scale_y_continuous(expand=c(0,0), limits = c(-3, 120)) + # makes the y-axis display as $
  theme(axis.text.x = element_text(size = 9.5), axis.title.y = element_text(size = 9.5, hjust = 0.6, vjust = 2.5), legend.position =c(0.8, 0.86), legend.text = element_text(size = 8), legend.key.size = unit(0.4, "cm"), legend.key.height = unit(0.4, "cm")) + #Legend theme
  guides(colour = guide_legend(override.aes = list(shape = 15, size=3))) +
  ylab("Daily predation(Barnacle eaten per day)") + # y-axis label
  xlab("") +
  ggtitle("") +
    annotate("text",
           x = 0.72,
           y = 0.15,
           label = "a",
           family = "", fontface = 3, size=3)+
     annotate("text",
           x = 1,
           y = 0.50,
           label = "b",
           family = "", fontface = 3, size=3)+
   annotate("text",
           x = 1.28,
           y = 0.42,
           label = "b",
           family = "", fontface = 3, size=3)+
  annotate("text",
           x = 1.72,
           y = 0.09,
           label = "a",
           family = "", fontface = 3, size=3)+
  annotate("text",
           x = 2,
           y = 0.34,
           label = "b",
           family = "", fontface = 3, size=3)+
  annotate("text",
           x = 2.27,
           y = 0.29,
           label = "b",
           family = "", fontface = 3, size=3)
  

boot_plot

#Confidence intervals 
field_exp_boot_summary<-field_exp_boot%>%
  group_by(Temperature, Treatment) %>%
  dplyr::summarize(mean(lowerci), mean(mean), mean(upperci))



#Figure 4: Effect of temperature feeding rates on the field  
png("Figures/Fig4_TemperaturePredation_Field_boot.png", width=15, height=12, units="cm", res=300)
print(boot_plot)
dev.off()
```
In the plot we can observed similar results that from our early plot however interval confidences are a lot smaller 


### Modelling lab experimetnal predation using same method 

```{r, message=FALSE, warning=FALSE}
# lets use lab_exp
# head(lab_exp)
# 
# 
# bootFUN <- function(model, newdata) {
#   if(class(model)[1] == "negbin"){
#     nr <- nrow(model[["model"]]) # count number of rows in the model (# of observations)
#     data <- model[["model"]] # pull data from model
#   } else {
#     nr <- nrow(model$data) # count number of rows in the model (# of observations)
#     data <- model$data # pull data from model
#   }
#   data2 <- data.frame(data[sample(1:nr, replace = TRUE), ]) # random sample of numbers from 1 - nr (# of rows) to select data from
#   update <- update(model, data = data2) # rerun the model using the 'new' dataset from the random smapling above
#   predict(update, newdata, type = "response", level = 0.95) # predicts response variable with model and updated data 
# }
# 
# bootnum <- 1000 #Number of boostraping 
# 
# #the model
# model_gamma<-glm((BarnacleEatenPerDay+0.001)~Treatment-1, family=Gamma(link="log"), data=lab_exp) # gamma model cannot consider 0
# summary(model_gamma)
# 
# 
# model_gamma$data
# 
# #the data 
# newdata <- data.frame(Treatment=lab_exp$Treatment)
# str(newdata)
# 
# 
# boot <- replicate(bootnum, bootFUN(model = model_gamma, newdata = newdata)) # run the bootFUN the number (bootnum) of times specified and save as matrix
# 
# str(lab_exp) 
# lab_exp$Treatment<-as.factor(lab_exp$Treatment)
# 
# #to find the estimate mean effect and the lower and upper confident intervals
# field_exp_boot <- cbind(field_exp, as.data.frame(t(apply(boot, 1, function(x) c(quantile(x, c(0.025, 0.5, 0.975)))))))
# 
# colnames(field_exp_boot)[9:11] <- c("lowerci", "mean", "upperci") # rename mean/CI columns
```

This system is not working so I am going to do something else

```{r}
# head(lab_exp)
# #The model
# model_gamma<-glm((BarnacleEatenPerDay+0.001)~Treatment-1, family=Gamma(link="log"), data=lab_exp)
# 
# 
# sample_coef_16C<-NULL
# sample_coef_21C<-NULL
# sample_coef_26C<-NULL
# sample_coef_28C<-NULL
# 
# sample.data<-lab_exp %>%
#   select(Treatment, BarnacleEatenPerDay) %>%
#   filter(Treatment=="16C")
# 
# 
# for(i in 1:2000) {
# #create a resampled dataset from the sample data
#    sample_d=sample.data[sample(1:nrow(sample.data), nrow(sample.data), replace=TRUE), ]
# 
#   #running the regression on these data 
#    #example model_bootstrap<-lm(y~x, data=sample_d)
#    model_gamma<-glm((BarnacleEatenPerDay+0.001)~Treatment-1, family=Gamma(link="log"), data=sample_d)
#    
#    #saving the coefficients
#    sample_coef_16C<-c(sample_coef_16C, model_bootstrap$coefficients[1])
#    
# #   sample_coef_21C<-c(sample_coef_21C, model_bootstrap$coefficients[2])
# #
#  #  sample_coef_26C<-c(sample_coef_26C, model_bootstrap$coefficients[3])
# 
#   # sample_coef_28C<-c(sample_coef_28C, model_bootstrap$coefficients[4])
# 
#  }
#  
#   boot_coefficient<-rbind(mean(sample_coef_16C), mean(sample_coef_21C), mean(sample_coef_26), mean(sample_coef_28))
# 
#  comparation_coef<-cbind(population.model$coefficients, sample.model$coefficients, boot_coefficient)
#  
# #comparation of coefficients between population, sample and boot
# # colnames(comparation_coef)<-c("Population", "Sample", "Boot")
# # comparation_coef
# # 
# # #they are relatevely similar
# # 
# # confint_population<-confint(population.model)
# # confint_sample<-confint(sample.model)
# # confint_boot<-confint(model_bootstrap)
# # 
#cbind(confint_populati
```


